\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-06 analysis/paper/paper.Rmd
starting a table with species and taxon info and counts

```{r setup, echo = FALSE}
library(bookdown)
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  dpi = 300
)
```

@@

```{r, results='hide', message=FALSE, include=FALSE}
# Extract hyperspectral reflectance data for each individual plant
#R/spectral-lib.Rmd
# Run the main analysis
```

@@

df <- data.frame(wavelength = c(347, 381, 382, 384),
                 number = c(94, 1220, 1733, 2922))

@@

>>>>

```{r setup, echo = FALSE}
library(bookdown)
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  dpi = 300
)
library(knitr)
```

@@

@@

```{r wavelengthTable, message = FALSE, echo = FALSE}
df <- data.frame(wavelength = c(347, 381, 382, 384),
                 number = c(94, 1220, 1733, 2922))

@@

```{r taxonTable, message = FALSE, echo = FALSE}
df <- data.frame(taxonCode = c("ABBA", "ABLAL", "ACRU, ACRUR", "ACSAS, ACSA3", 
                               "AMLA", "ARTR2", "BELE", "BENE4"),
                 scientificName = c("Abies balsamea", 
                                    "Abies lasiocarpa",
                                    "Acer rubrum",
                                    "Acer saccharum", 
                                    "Amelanchier laevis",
                                    "Artemisia tridentata",
                                    "Betula lenta",
                                    "Betula neoalaskana"),
                 commonName = c("balsam fir", "subalpine fir", "red maple", "sugar maple",
                                "Allegheny serviceberry", "sagebrush", "sweet birch", "resin birch"),
                 count = c(47,117, 489, 79, 37, 494, 28, 35))

knitr::kable(x = df, 
             # set column names
             col.names = c("Taxon code",
                           "Scientific name",
                           "Common name",
                           "Number of spectra"),
             # center align text in the columns
             align = c("c", "c", "c", "c"),
             format = "simple")
```
